Precise Asymptotics of Information Transfer in Two-layer Linear Neural Networks

### 2021-06-30 revision_journal/setup.tex
Updates from Overleaf

\subsection{Large dimensional random matrices}

Consider the transfer learning setting with two data sets. We denote their sample sizes by $n_1$ and $n_2$.
For $i=1,2,$ let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates. We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise:
$$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)},\quad i=1,2.$$
Throughout the paper, we make the following assumptions on the feature covariates $X^{(i)}$ and the noise vectors $\varepsilon^{(i)}$, following the work of \citet{hastie2019surprises} (see also \citet{wu2020optimal,richards2021asymptotics} and the references therein). %We remark that all these assumptions are natural in high-dimensional statistics.

We assume that the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)}$. More precisely, let
\be\label{XofZ}X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p},\quad i=1,2, \ee
where each $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are $p\times p$ deterministic positive definite symmetric matrices, and $Z^{(1)}=(z^{(1)}_{ij})$ and $Z^{(2)}=(z^{(2)}_{ij})$ are $n_1\times p$ and $n_2\times p$ random matrices with real i.i.d. entries satisfying
\begin{equation}\label{assm1}
\mathbb{E} z^{(1)}_{ij}=\mathbb{E} z^{(2)}_{ij} =0, \ \quad \ \mathbb{E} \vert z^{(1)}_{ij} \vert^2=\mathbb{E} \vert z^{(2)}_{ij} \vert^2 =1,
\end{equation}

Furthermore, we assume that the entries $z^{(1)}_{ij}$ and $z^{(2)}_{ij}$ have finite $\varphi$-th moment for some constant $\varphi>4$:
\be \label{conditionA2}
\mathbb{E} \vert z^{(1)}_{ij} \vert^\varphi  \le \tau^{-1},\quad \mathbb{E} \vert  z^{(2)}_{ij} \vert^\varphi   \le \tau^{-1}
\ee
for a small constant $\tau>0$. We assume that $\Sig^{(i)}$ has eigendecomposition
\be\label{eigen}
\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
\ee
where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
\begin{equation}\label{assm3}
 \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
\ee
%for a small constant $\tau>0$.

We assume that $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are two independent random noise vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moment up to any order: for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
\be\label{eq_highmoments}
\E  | \ve^{(1)}_{i} |^k \le C_k,\quad \E  | \ve^{(2)}_{i} |^k \le C_k.
\ee
Finally, we assume that $\beta^{(1)}$ and $\beta^{(2)}$ are two arbitrary deterministic or random vectors that are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$.
%Moreover, we assume that
%\be\label{eq_SNR}
%\tau\le \frac{\|\beta^{(1)}\|^2}{\|\beta^{(2)}\|^2} \le \tau^{-1},\quad  \frac{\|\beta^{(1)}\|^2}{\sigma^2} \ge \tau,
%\ee
%for a small constant $\tau >0$. The first condition means that the norms of the two model parameters $\beta^{(1)}$ and $\beta^{(2)}$ are comparable, while the second condition means that the singal-to-noise ratio cannot be too small.

In this paper, we consider the high-dimensional setting, where the sample ratios satisfy that  %We assume that the aspect ratios $d_1:= p/n_1$ and $d_2:=p/n_2$ satisfy that
\be\label{assm2}
1+\tau \le \rho_1:=\frac{n_1}{p} \le p^{\tau^{-1}}, \quad 1+\tau \le \rho_2:=\frac{n_2}{p} \le p^{\tau^{-1}}, \quad \tau \le \frac{\rho_1}{\rho_2}\le \tau^{-1},
\ee
for a small constant $\tau >0$. If $\rho_i>p^{\tau^{-1}}$, $i=1,2$, we are basically in the low-dimensional region, where the law of large numbers and central limit theorem already  give good enough results without using the theory developed in this paper. The lower bounds $\rho_1> 1+\tau$ and ${\rho_2 > 1+ \tau}$
are to ensure that the sample covariance matrices $  (X^{(1)})^\top X^{(1)} $ and $  (X^{(2)})^\top X^{(2)} $ are non-singular with high probability, so that the ordinary least squares (OLS) estimator is well-defined for the linear regression problem on each task.

We summarize our basic assumptions here for future reference.
\begin{assumption}\label{assm_big1}
Let $\tau$ be a small constant.
\begin{enumerate}
\item  $X^{(1)}$ and $X^{(2)}$ take the form \eqref{XofZ}, where $Z^{(1)}$ and $Z^{(2)}$ are respectively $n_1\times p$ and $n_2\times p$ random matrices with i.i.d. entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig^{(1)}$ and $\Sig^{(2)}$ are deterministic positive definite symmetric matrices satisfying \eqref{eigen} and \eqref{assm3}. %and (\ref{assm2}). We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).

\item $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are random vectors independent from $X^{(1)}$ and $X^{(2)}$, and with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.

\item $\beta^{(1)}$ and $\beta^{(2)} $ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)} $. %, and satisfy \eqref{eq_SNR}.

\item $\rho_{1}$ and $\rho_{2}$ satisfy \eqref{assm2}.

\end{enumerate}
\end{assumption}

\subsection{Hard parameter sharing estimators}

%\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}
Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{bastani2020predicting, li2020transfer}:
$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$

Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
The critical questions are:
(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?

In this paper, we measure the performance of $\hat{\beta}_2^{\MTL} (\hat a)$ through the out-of-sample predication loss (test error). Consider a test data point $(x,y)$ generated from the same model as task 2: $y= x^\top \beta^{(2)} + \ve$, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable. We want to use $x^\top \hat{\beta}_2^{\MTL} (\hat a) $ to predict $y$, and we measure the predication loss using the mean squared error
$$\exarg{x}{\left\|y-x^\top \hat{\beta}_2^{\MTL} (\hat a) \right\|^2}= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 + \sigma^2.  $$
Since $\sigma^2$ is a constant that does not depend on the model, we ignore it and define the predication loss as
\be\label{HPS_loss}
L(\hat{\beta}_2^{\MTL}(\hat a)):= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 .
 \ee
We will compare it to the out-of-sample predication losses of the baseline estimators, $L(\hat{\beta}_2^{\STL})$ and $L(\hat{\beta}^{\AV}(\lambda))$ for some properly chosen $\lambda\in [0,1]$.

%$L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator  as a baseline.

Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
\begin{align}
L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
&\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
\end{align}
Note that if we replace $\hat a$ with a fixed number $a$ in \eqref{Lbeta_HPS}, then taking the expectation over $\ve^{(1)}$ and $\ve^{(2)}$, we can get a clean bias-variance decomposition of the predication loss:
\be\label{partial-L} \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}(a)) } = L_{\bias} (a) + L_{\var}(a),\ee
where
\be\label{Lbias} L_{\bias} (a) := \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2 \ee
is called the bias term, which depends on the model bias between task 1 and task 2, and
\be\label{Lvar}  L_{\var}(a):=\sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }} \ee
is called the variance term, which depends on the noise variance. Using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma. In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
%predication loss for the HPS and OLS estimators.

\begin{lemma}\label{lem_HPS_loss}
 Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$:
\begin{align}
L(\hat{\beta}_2^{\MTL}(a)) &=\left[ 1+ \OO(p^{-1/2+c})\right]\cdot \left[L_{\bias} (a) + L_{\var}(a)\right] \nonumber\\
&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right], \label{L_HPS_simple}
\end{align}
\begin{align}
L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
& + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
\end{align}
and
\begin{align}
L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
\end{align}
%Moreover, there exists a constant $C_0>0$ such that with high probability,
%\be\label{loss_large}
%g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
%\ee
%with high probability for any small constant $\e>0$.
\end{lemma}

@@

>>>>

\subsection{Data model}

We describe the data model and the underlying assumptions.
Suppose we have two regression datasets.
We denote their sample sizes by $n_1$ and $n_2$, respectively.
Consider either $i = 1$ or $i = 2$.
Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for the feature covariates $X^{(i)}$ follows a linear model plus random noise $\varepsilon^{(i)}$:
$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)}.$
Both $\beta^{(1)}$ and $\beta^{(2)}$ are two arbitrary deterministic or random vectors that are independent of the feature covariates and the noise vector.
Throughout the paper, we make the following assumptions on  $X^{(i)}$ and  $\varepsilon^{(i)}$, which are standard in recent  random matrix theory literature (see e.g. \citet{tulino2004random,bai2010spectral}). %We remark that all these assumptions are natural in high-dimensional statistics.

First, we assume the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)} \in \real^{p \times p}$. More precisely, let
\be\label{XofZ}
    X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p},
\ee
where $\Sigma^{(i)}$ is a deterministic positive definite symmetric matrices, $Z^{(i)}=(z^{(i)}_{j,k})$ is a $n_i\times p$ random matrix with real-valued independent entries having zero mean and unit variance.
%\begin{equation}\label{assm1}
%\mathbb{E} z^{(1)}_{ij}=\mathbb{E} z^{(2)}_{ij} =0, \ \quad \ \mathbb{E} \vert z^{(1)}_{ij} \vert^2=\mathbb{E} \vert z^{(2)}_{ij} \vert^2 =1,
%\end{equation}
Let $\tau>0$ be a small constant.
We assume that for some constant $\varphi>4$, the $\varphi$-th moment of each entry $z^{(i)}_{j, k}$ is bounded from above by $1/\tau$:
\be \label{conditionA2}
\ex{\vert z^{(i)}_{j, k} \vert^\varphi}  \le \frac 1{\tau}. %,\quad \mathbb{E} \vert  z^{(2)}_{ij} \vert^\varphi   \le \tau^{-1}
\ee

Second, we assume that $\varepsilon^{(i)} \in \real^{n_i}$ is a random noise vector with i.i.d entries having mean zero, variance $\sigma^2$, and bounded moment up to any order: for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
\be\label{eq_highmoments}
\ex{| \ve^{(i)}_{j} |^k} \le C_k.
\ee

%Moreover, we assume that
%\be\label{eq_SNR}
%\tau\le \frac{\|\beta^{(1)}\|^2}{\|\beta^{(2)}\|^2} \le \tau^{-1},\quad  \frac{\|\beta^{(1)}\|^2}{\sigma^2} \ge \tau,
%\ee
%for a small constant $\tau >0$. The first condition means that the norms of the two model parameters $\beta^{(1)}$ and $\beta^{(2)}$ are comparable, while the second condition means that the singal-to-noise ratio cannot be too small.

Finally, we assume a high-dimensional setting when the sample sizes are proportional to the dimension up to a constant factor.
Denote by $\rho_i = n_i / p$, we require that
\be\label{assm2}
1+\tau \le \rho_i \le p^{\tau^{-1}}.
\ee
The first inequality ($1 + \tau \le \rho_i$) ensures that the sample covariance matrices $(X^{(1)})^\top X^{(1)}$ and $(X^{(2)})^\top X^{(2)}$ are non-singular with high probability.
%Thus, the ordinary least squares estimator is well-defined for the linear regression problem on each (single) task.
%This setting encompasses many 
The second inequality ($\rho_i \le p^{\tau^{-1}}$) is without loss of generality.
Otherwise, standard concentration results such as the central limit theorem already imply accurate estimates of the linear model under the setting defined by equation \eqref{assm2}.

To summarize, the underlying assumptions in our data model are as follows.
\begin{assumption}[Data model]\label{assm_big1}
Let $\tau$ be a small constant.
Let $\Sig^{(1)}$ and $\Sig^{(2)}$ are deterministic positive definite symmetric matrices whose eigenvalues are bounded between $\tau$ and $1 / \tau$.
\begin{enumerate}
\item  $X^{(1)}$ and $X^{(2)}$ take the form of equation \eqref{XofZ}, where $Z^{(1)}$ and $Z^{(2)}$ are both random matrices with i.i.d. entries having zero mean, unit variance, and bounded moments as in equation \eqref{conditionA2}.

\item $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are random vectors independent from $X^{(1)}$ and $X^{(2)}$, and with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in equation \eqref{eq_highmoments}.

\item $\rho_{1}$ and $\rho_{2}$ satisfy equation \eqref{assm2}. Furthermore, $\tau \le \frac{\rho_1}{\rho_2}\le \tau^{-1}$.
\end{enumerate}
\end{assumption}

%\item $\beta^{(1)}$ and $\beta^{(2)} $ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)} $. %, and satisfy \eqref{eq_SNR}.

\todo{
We assume that $\Sig^{(i)}$ has eigendecomposition
\be\label{eigen}
\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
\ee
where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
\begin{equation}\label{assm3}
 \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
\ee}
%for a small constant $\tau>0$.

\subsection{Estimators}

We describe our estimators that combine the information from both datasets.
We learn a two-layer linear neural network with parameters $A \in \real^{p\times r}$, $B_1 \in \real^{r}$, and $B_2 \in \real^r$ by minimizing the following optimization objective:
\begin{align}\label{eq_hps}
    f(A, B_1, B_2) = \bignorm{X^{(1)} A B_1 - Y^{(1)}}_2^2 + \bignorm{X^{(2)} A B_2 - Y^{(2)}}_2^2.
\end{align}
The above two-layer neural network (also called hard parameter sharing \cite{C97}) captures the intuition that both datasets share the feature space (i.e. the subspace spanned by the columns of $A$) while each having a separate prediction head.
Suppose that $(\hat{A}, \hat{B_1}, \hat{B_2})$ is a minimizer of $f(\cdot)$.
We define the hard parameter sharing estimator for task $i$ as
\[ \hat{\beta}_i^{\MTL} \define \hat{B} \hat{A}_i. \]
Our study of such estimators is motivated by the fact that hard paratemer sharing is widely used in empirical studies of multi-task learning \cite{R17}.
\todo{Later on in Section \ref{sec_diff}, we will further compare the HPS estimator to other natural transfer learning estimators.} %$L(\hat{\beta}_2^{\STL})$ and $L(\hat{\beta}^{\AV}(\lambda))$ for some properly chosen $\lambda\in [0,1]$.}

We measure the performance of $\hat{\beta}_i^{\MTL}$ through the out-of-sample predication risk (or test loss).
Consider a datapoint $(x,y)$ generated from the same model as dataset $i$: $y= x^\top \beta^{(i)} + \ve$. %, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable.
%We want to use $x^\top \hat{\beta}_2^{\MTL} (\hat a) $ to predict $y$, and we measure
The expected predication risk (under mean squared error) is given by
$$\exarg{x, \varepsilon}{\left\|y-x^\top \hat{\beta}_i^{\MTL} \right\|^2}= \left\|\big(\Sigma^{(i)}\big)^{1/2} \left(\hat{\beta}_i^{\MTL} - \beta^{(i)}\right)\right\|^2 + \sigma^2.$$
%Since $\sigma^2$ is a constant that does not depend on the model, we ignore it and define the predication loss as
The excess risk is defined without the constant term $\sigma^2$:
\be\label{HPS_loss}
    L(\hat{\beta}_i^{\MTL}):= \left\| \big(\Sigma^{(i)}\big)^{1/2} \left(\hat{\beta}_i^{\MTL} - \beta^{(i)}\right)\right\|^2 .
\ee

We focus on the setting where the hidden dimension $r = 1$.
Otherwise, the excess risk of the HPS estimator and that of the ordinary least squares (OLS) estimator are equal to each other \cite{WZR20}.
\begin{proposition}\label{prop_large_r}
    Suppose that Assumption \ref{assm_big1} holds.
    Let $\hat{\beta}_i^{\STL} = \big( {X^{(i)}}^{\top} X^{(i)} \big)^{-1} {X^{(i)}}^{\top} Y^{(i)}$ denote the OLS estimator, for either $i = 1$ or $i = 2$.
    Then, for any $r \ge 2$, we have that $L(\hat{\beta}_i^{\MTL}) = L(\hat{\beta}_i^{\STL})$.
\end{proposition}

\begin{proof}
    Since both $n_1$ and $n_2$ are at least $(1 + \tau) p$, the inverse of both ${X^{(1)}}^{\top} X^{(1)}$ and ${X^{(2)}}^{\top} X^{(2)}$ exists.
    Thus, both $\hat{\beta}_1^{\STL}$ and $\hat{\beta}_2^{\STL}$ are well-defined.
    The global minimum of each summand of equation \eqref{eq_hps} is achieved if and only if $\hat{\beta}_1^{\STL}$ and $\hat{\beta}_2^{\STL}$ are both in the column subspace of $A$.
    In this case, $\hat{\beta}_1^{\MTL} = A B_1$ must be equal to $\hat{\beta}_1^{\STL}$ (same for $\hat{\beta}_2^{\MTL}$).
\end{proof}
%Our goal is to characterize the 
%$The minimizers of $f(\cdot)$
%\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}

When $r = 1$, both $B_1$ and $B_2$ reduce to scalars.
In particular, the case when $B_1$ and $B_2$ are both equal to $1$ reduces to a pooling estimator, which treats both datasets as if they are drawn independently from the same distribution.
Such pooling estimators have been shown to be effective on e-commence and healthcare datasets \cite{bastani2020predicting}.
Additionally, they have been used as a preprocessing step of minimax optimal estimators, under certain conditions of the data \cite{li2020transfer} (see also Section \ref{sec_related} for further discussion of both works).
%Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{, li2020transfer}:
%$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$

%Given a solution from minimizing $f(A, B)$, denoted by   (which we will specify below), let  denote the HPS estimator for task $i$.
%The critical questions are:
%(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
%(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?

%$L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator  as a baseline.
\subsection{Bias and variance}

Proposition \ref{prop_large_r} suggests that the two-layer neural network provides information transfer only when $r = 1$.
Next, we provide the bias-variance decomposition of $L(\hat{\beta}^{\MTL}_2)$ under this setting.
As a remark, for general $r$, problem \eqref{eq_hps} is non-convex since $f(\cdot)$ is a degree-four polynomial.
Nevertheless, the setting when $r = 1$ remain tractable since we can write a closed-form solution of $A$ given any (scalar) $B_1$ and $B_2$.

\begin{proposition}\label{lem_HPS_loss}
     Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$:
    \begin{align}
    L(\hat{\beta}_2^{\MTL}(a)) &=\left[ 1+ \OO(p^{-1/2+c})\right]\cdot \left[L_{\bias} (a) + L_{\var}(a)\right] \nonumber\\
    &+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right], \label{L_HPS_simple}
    \end{align}
    \begin{align}
    L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
    &+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
    & + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
    \end{align}
    and
    \begin{align}
    L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
    \end{align}
    %Moreover, there exists a constant $C_0>0$ such that with high probability,
    %\be\label{loss_large}
    %g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
    %\ee
    %with high probability for any small constant $\e>0$.
\end{proposition}

\begin{proof}[Proof sketch]
    Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
    \begin{align}
    L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
    &\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
    \end{align}
    Note that if we replace $\hat a$ with a fixed number $a$ in \eqref{Lbeta_HPS}, then taking the expectation over $\ve^{(1)}$ and $\ve^{(2)}$, we can get a clean bias-variance decomposition of the predication loss:
    \be\label{partial-L} \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}(a)) } = L_{\bias} (a) + L_{\var}(a),\ee
    where
    \be\label{Lbias} L_{\bias} (a) := \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2 \ee
    is called the bias term, which depends on the model bias between task 1 and task 2, and
    \be\label{Lvar}  L_{\var}(a):=\sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }} \ee
    is called the variance term, which depends on the noise variance. Using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma. In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
    %predication loss for the HPS and OLS estimators.
\end{proof}

@@

\todo{clarify overparametrize}
As a clar,  following the work of \citet{hastie2019surprises} (see also \citet{bartlett2020benign} and the references therein)
